%%%%%%%%%%%%%%%%%%%%%% 1 %%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Undergraduates and Part-Time Jobs [22 points]}\label{sec:jobs}
According to the California Center for Overextended Students, $\STANFORDRATE{}$\% of Stanford undergraduates and $\BERKELEYRATE{}$\% of Berkeley undergraduates maintain part-time jobs in addition to their coursework, all independently of each other.

\begin{enumerate}[label=\alph*.]

%%%%%%%%%%%%%%%%%%%%%%
\item (4 points) You interview five Stanford undergraduates and five Berkeley undergraduates.  What is the probability that exactly nine of the ten hold part-time jobs?
	
		
		\answernumeric{.2\paperheight}{}{\vspace*{1em}}{problems/bernoulli_soln_a}
		

%%%%%%%%%%%%%%%%%%%%%%
\item (5 points) Assume you interview Stanford undergraduates, one after another, to survey who holds a part-time job. Let $S_k$ be the number of Stanford undergraduate that must be interviewed until you find the $k^{th}$ student who holds a part-time job.  What is $P(S_{\NSUCCESSES{}} = \NTRIALS{})$? 
	
		\answernumeric{.3\paperheight}{}{\problempagebreak{1}}{problems/bernoulli_soln_b}

%%%%%%%%%%%%%%%%%%%%%%
\item (7 points) Suppose there are 7000 Stanford undergraduates and 33000 Berkeley undergraduates, and you choose two students at random from the 40000 combined and learn they each have part-time jobs. What is the conditional probability that both students attend Berkeley, given both have part-time jobs?
	
		\answernumeric{.2\paperheight}{}{\vspace*{1em}}{problems/bernoulli_soln_c}


%%%%%%%%%%%%%%%%%%%%%%
\item (6 points) Suppose you interview $\SAMPLESIZE{}$ Stanford undergraduates individually.  What is the approximate probability that strictly more than $\THRESHOLD{}$ of them hold part-time jobs?
	
		\answernumeric{.3\paperheight}{}{\vspace*{0em}}{problems/bernoulli_soln_d}

\end{enumerate}