%%%%%%%%%%%%%%%%%%%%%% 3 %%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Fish Sticks [12 points]}\label{sec:fish}
Fish Sticks (a frozen meal company) wants to analyze the success of their new home-delivery website. Suppose users independently visit the homepage at an average rate of $\FISHRATE{}$ users per minute.

\begin{enumerate}[label=\alph*.]

%%%%%%%%%%%%%%%%%%%%%%
\item (2 points) What is the expected number of users who visit the homepage in the next $\FISHSCALE{}$ minutes?
	
		
		\answernumeric{.09\paperheight}{users}{\vspace*{1em}}{problems/poisson_soln_a}
		

%%%%%%%%%%%%%%%%%%%%%%
\item (4 points) What is the probability that there are exactly $\FISHNUM{}$ users who visit the homepage in the next $\FISHSCALE{}$ minutes?
	
	
		\answernumeric{.2\paperheight}{}{\vspace*{1em}}{problems/poisson_soln_b}

\end{enumerate}


Each user that visits the homepage downloads exactly $\FISHSCALE{}$ MB of website data. We define \textbf{homepage load} in a minute to be the total amount of website data downloaded across all users who visit the homepage in that minute, e.g., 10 homepage visitors in the next minute means the homepage load in that minute is $\FISHSCALE{}0$ MB. As before, users still independently visit the homepage at an average rate of $\FISHRATE{}$ users per minute.

\begin{enumerate}[label=\alph*.]
\setcounter{enumi}{2}

%%%%%%%%%%%%%%%%%%%%%%
\item (2 points) What is the expected homepage load in the next minute?
	
		\answernumeric{.09\paperheight}{MB}{\problempagebreak{2}}{problems/poisson_soln_c}


%%%%%%%%%%%%%%%%%%%%%%
\item (4 points) What is the probability that the homepage load is exactly $\FISHNUM{}$ MB in the next minute?
	
		\answernumeric{.3\paperheight}{}{\vspace*{0em}}{problems/poisson_soln_d}


\end{enumerate}